Measuring Political Freedom Around the World

### 2020-11-13 slides.Rmd
plots and plots

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE) 
```

@@

```{r}
data %>% 
  group_by(polrights_fh) %>% 
  add_count(polrights_fh) %>% 
  ggplot() + 
  geom_bar(aes(x = polrights_fh)) + 
  geom_text(aes(x = polrights_fh, y = n, label = n)) + 
  scale_x_continuous(breaks = 1:7) + 
  theme_test()
```

@@

```{r}
broom::tidy(model_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  kable(col.names = c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"))

```

@@

---
# Remedial measures
```{r}
model_df5 %>% 
  broom::augment() %>% 
  ggplot() + 
  geom_histogram(aes(.resid), bins = 200) +
  scale_x_continuous(limits = c(-4,4))

```

---
# Remedial measures

```{r}
model_df5 %>% 
  broom::augment() %>% 
  mutate(yhat = predict(model_df5)) %>% 
  ggplot() + 
  geom_point(aes(x = yhat, y = .resid)) + 
  geom_hline(yintercept = 0, color = "red") + 
  scale_y_continuous(limits = c(-4,4))
```

@@

>>>>

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
theme_set(theme_light(base_size = 30))
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE, fig.width=12, fig.height=8) 
```

@@

---
class: center, middle
```{r}
data %>% 
  group_by(polrights_fh) %>% 
  add_count(polrights_fh) %>% 
  ggplot() + 
  geom_bar(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "black") +

  geom_text(aes(x = polrights_fh, y = n, label = n), vjust = -.75) + 
  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
  scale_x_continuous(breaks = 1:7) + 
  theme_test(base_size = 30) + 
  theme(legend.position="none")
```

@@

```{r}
broom::tidy(model_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  kable(col.names = c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) 
```

@@

---
# F-Test on life expectancy

@@

class: center, middle
# Remedial measures
```{r warning=FALSE}
hist + qq  
```

---
class: center, middle
# Remedial measures
```{r message=FALSE}
labeled_outliars + labeled_qq
```

# Remedial measures

```{r}
model_df5 %>% 
  broom::augment() %>% 
  mutate(yhat = predict(model_df5),
         resid = resid(model_df5)) %>% 
  ggplot() + 
  geom_point(aes(x = yhat, y = resid)) + 
  geom_hline(yintercept = 0, color = "red") + 
  scale_y_continuous(limits = c(-4,4))
```

# Brown - Forthe
